\documentclass{article}
\usepackage{amsbsy,amscd,amsfonts,amsgen,amsmath,amsopn,amssymb,amstext,amsthm,amsxtra}
\usepackage{graphicx}
\usepackage{verbatim}
\usepackage{multicol}
\usepackage{fullpage}
\begin{document}

\title{Function Drills with Answers}
\author{Statistics 405}
\date{\today}
\maketitle

%-------------------------------------------------------------------
% Begin entering your LaTeX document content here...

\noindent Write a simple function in R for each of the following tasks. 
\begin{enumerate}

\item Return the circumference of a circle with the given radius.

\item Return the area of a circle with the given radius.

\item Return the area of a circle with the given radius.

\item Return the circumference, area (of the largest cross-section), and volume of a sphere with the given radius. Each should be labelled in the functions output.

\item Given the coefficients of a quadratic polynomial, return the roots.

\item Return the lowest positive value of a vector

\item Return the second lowest positive value of a vector

\item Divide each element in a numeric vector by the vector's length.

\item Test whether a number is even.

\item Test whether a number is odd.

\item If a number is odd add one to it.

\item If any number in a numeric vector is odd, add one to it

\item Test whether a number is an integer.

\item Find the range of a vector.

\item Find the sum of a numeric vector (without using \verb!sum()!).

\item Find the mean of a numeric vector (without using \verb!mean()!).

\item Find the mean of a vector that contains one or more NA's by ignoring any NA's (without using \verb!mean()!).

\item Find the variance of a numeric vector (without using \verb!var()!).

\item Automatically create a histogram of a vector.

\item Automatically create a histogram of a vector with the given number of bins.

\item Automatically create a scatterplot matrix with the variables in a given data frame.

\item Find the least common multiple of two numbers.

\item Index a series of observations by the first observation (hint: express each observation as a percentage of the first observation).

\item Find the determinant of a four by four matrix.

\item Separate the integer and decimal parts of a number, return them in a vector of length two.

\item Return the given vector with all NA's removed.

\item Return the row numbers of rows in a data frame that contain NA's.

\item Return the actual rows of a data frame that contain NAÕs. 

\item Create a new vector by repeating a given vector a given number of times.

\item Double each element in a vector (e.g., turn \emph{a,b,c,...} into \emph{a, a, b, b, c,...}).

\item Randomly return one of the following phrases, ``Ace", ``King" or ``Queen" with equal probability of returning each.

\item Randomly return one of the following phrases, ``Ace", ``King" or ``Queen" with twice as much probability of returning ``Ace" as either ``King" or ``Queen."

\item Take any character string and add ``...in Stat 405" to the end.

\item Take any character string and add ``...in Stat 405" to the end. Check that the input is a character string. Return an error if it is not.

\item Save the current graph with width = 6 and height = 6 as a pdf with the inputted name.

\item Save the current graph with a given width and height as a pdf with the inputted name.

\item Save a copy of a data frame as a comma separated values file whose filename is the name of the data frame plus ".csv"

\item Identify whether an object is a logical, character, or numeric object.

\item Display the number of groups of size n can be made from the inputted vector of length k.

\item Return the number of unique permutations that can be from a given vector (caution: don't use large vectors).

\item Return the number of unique sets that can be made from an inputted vector.

\item Return whichever the entered number is closest to: 0 or 1000.

\item Given a data frame with two columns, return all of the combinations of the two variables that occur once or more.

\item Automatically plot the above results with each variable on an axis and the number of occurrences (counts) represented by color.

\item Create a new vector where each \emph{ith} element is the sum of the first \emph{i} elements of the given vector.

\item Select the number in a vector that is the greatest distance from the first element of the vector

\item Return whether a vector of numbers is right skewed or left skewed by comparing its mean and median.

\item Find the (statistical) mode of a vector.
\item Given a numeric vector of length 100, determine which element occurs at the 70th percentile.
\item Given a numeric vector of length 10, determine which element occurs at the 70th percentile.
\item Given a numeric vector of length 10, determine which element occurs at the 70th percentile.
\item Return a vector with its elements reordered in a random manner.
\item Return a vector with its elements ordered from smallest to largest.
\item Return a vector with its elements ordered largest to smallest.






\end{enumerate}


\end{document}
